---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r Setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%"
)
```

# eqt

## Overview

The **eqt** package contains a collection of tools commonly used to perform **small-sample equating**. The following transformations are possible:

* Identity
* Mean
* Linear
* Circle-arc

If anchor items are included, then any of the following methods may be applied:

* Nominal weights
* Tucker
* Levine observed-score
* Levine true-score
* Chained

## Installation

Install the development version from GitHub.

```{r GitHub, message = FALSE}
# install.packages("devtools")
devtools::install_github("kyliegorney/eqt")
```

## Example: Random Groups Design

In the following examples, consider a 100-item test that is taken by 25 examinees. Use the data stored in the object `random_groups_dat`, and let `x` and `y` be the item responses from the new and old forms, respectively.

```{r eqt random groups}
library(eqt)

# Extract data
list2env(random_groups_dat, envir = globalenv())

# Identity equating
(id <- eqt(x, y))

# Mean equating
(me <- eqt(x, y, linear = "mean"))

# Linear equating
(li <- eqt(x, y, linear = "linear"))
```

Individual equatings may be combined to form a weighted result using `multipleqt()`.

```{r multipleqt}
(id_li <- multipleqt(id, li))
```

Use `boot()` to compute the bootstrap standard errors.

```{r boot}
# Use an eqt object
set.seed(1004)
boot(li)

# Use a multipleqt object
set.seed(1004)
boot(id_li)
```

## Example: Common-Item Nonequivalent Groups Design

In this example, suppose the two test forms have the first 30 items in common. Use the data stored in the object `nonequiv_groups_dat`, and let `x` and `y` be the item responses from the new and old forms, respectively.

```{r eqt nonequiv groups}
# Extract data
list2env(nonequiv_groups_dat, envir = globalenv())

# Tucker mean equating
eqt(x, y, xv = 1:30, yv = 1:30, linear = "mean", method = "tucker")

# Levine observed-score equating with an external anchor
eqt(x, y, xv = 1:30, yv = 1:30, linear = "linear", method = "levine observed",
    anchor = "external")

# Simplified circle-arc with chained linear equating
eqt(x, y, xv = 1:30, yv = 1:30, linear = "linear", method = "chained",
    circle = "simplified")
```
